---
title: "REDRESS: Baseline data collection"
subtitle: "Initial exploration"
author: 
  - "Lucas Sempe & Yan Ding"
date: '`r Sys.Date()`'
output:
  xaringan::moon_reader:
    css: xaringan-themer.css
    nature:
      slideNumberFormat: "%current%"
      highlightStyle: github
      highlightLines: true
      ratio: 16:9
      countIncrementalSlides: true
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
knitr::opts_chunk$set(
  fig.width=9, fig.height=3.5, fig.retina=3,
  out.width = "100%",
  cache = FALSE,
  echo = FALSE,
  message = FALSE, 
  warning = FALSE,
  hiline = TRUE
)
```

```{r xaringan-themer, include=FALSE, warning=FALSE}
library(xaringanthemer)

style_duo_accent(
  primary_color = "#00226B",
  secondary_color = "#CD122D",
  header_font_google = google_font("Josefin Sans"),
  text_font_google   = google_font("Montserrat", "300", "300i"),
  code_font_google   = google_font("Fira Mono"),
  text_font_size = ".8rem"
)

source("Health_Facilities_pages_1_2_3.R")

```

## General information

.right-column[

During May 2022, 8 member of the REDRESS Liberia collected data from health facilities, health workers and patients across 3 counties.

Data was collected from 56 health facilities: 44 clinics, 8 health centers and 4 hospitals

6 health facilities provide surgical procedure for hydrocele
]


.left-column[
```{r}

knitr::kable(hfs.unique %>% group_by(County) %>% tally () %>% 
                    rename(HF=n), format = 'html')

```
]

---
## General information
```{r}

hfs.unique %>%   mutate(District=as.factor(District),
  District = fct_relevel(District, 
            "Cavalla", "Tchien", "Foya", 
            "Voinjama", "Firestone", "Mambah-Kaba")) %>%
  ggplot(aes(District,fill=County)) + geom_bar() +
    scale_xaringan_fill_discrete() + theme_light() + ylab("Number of Health Facilities")


```

---
## General information

.left-column[
REDRESS found 46 cases registered in ledgers across 13 health facilities

43 facitilies without cases in 1 year
]


.right-column[
```{r}

knitr::kable(hfs.unique %>% group_by(County,health_facility) %>% 
  summarise (t=sum(X3...Number.of.NTD.patients.,na.rm = T)) %>% 
  filter (t>0) %>% 
  arrange (-t) %>% rename(HF = health_facility,
                          `Number cases`=t), format = 'html')

```
]

---
## Information per Health Facility

```{r eval=requireNamespace("DT", quietly=TRUE)}
DT::datatable(dd, fillContainer = FALSE, options = list(pageLength = 3),
              rownames = FALSE,
               caption = 'Table 1: Number of NTDs registered cases',
              filter = 'top',
              colnames = c('County', 'District', 'HF', 'REDRESS', 'HMIS 19',
                           'HMIS 20', 'Total HMIS' ))
```

---

## Comparison between HMIS '19 & '20 and REDRESS

.center[
```{r, fig.width=9, fig.height=6.5}

p<-dd %>%    arrange(Baseline_REDRESS) %>%    # First sort by val. This sort the dataframe but NOT the factor levels
  mutate(HF=factor(HF, levels=HF)
         ) %>%
    ggplot() + 
  geom_point(aes (HF,hmis20_19,colour="HMIS"),
             position=position_jitter(width = 0.1))+
  geom_point(aes (HF,Baseline_REDRESS,colour="REDRESS")) + theme_light() + 
   theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1, size=5)) + 
  facet_wrap(~County, scales = "free_x") + ylab ("") + xlab ("") + 
  labs(colour="Data") + 
  theme (legend.position = "bottom") + scale_xaringan_colour_discrete()


ggplotly(p,tooltip = c("HF", "Baseline_REDRESS","hmis20_19")) 

```
]

---
## Cases

.right-column[

Onchocerciasis has the highest number (14), followed by Hidrocele (12) and Buruli ulcer (10)

No cases found of Lymphedema

Foya (19) and Voinjama (12) in Lofa represent 73% of cases.

Margibi has 5 cases and Grand Gedeh has 6 in Cavalla. 

No cases found in Tchien (Grand Gedeh)

]


.left-column[

```{r}

knitr::kable(p2 %>% group_by(Disease) %>% summarise(Cases=sum(n)), format = 'html')

```

<br>

```{r}
knitr::kable(p2 %>% group_by(District) %>% summarise(Cases=sum(n)), format = 'html')

```


]

---
## Cases by district

```{r fig.width=9, fig.height=6.5}

plot2<-p2 %>% ggplot(aes(health_facility=health_facility)) + geom_jitter(aes(District,n,colour=County),
                            width=.1) +theme_light() + 
  facet_wrap(~Disease) + # no cases in Tchien 
 scale_y_continuous(breaks = seq(1,12,2)) + # no cases of Lymphedema
theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1, size=5)) +
   
   theme (legend.position = "bottom") + scale_xaringan_colour_discrete()
  
ggplotly(plot2,tooltip = c("health_facility", "n"))
```



---
## Health workers (from HFs data)

.left-column[
1430 health workers were identified across 56 health facilities.

Lofa have 621 hws, followed by Margibi (475) and Grand Gedeh (234)

There is no clear relationship between number of cases and total number of health workers.

]

.right-column[
```{r}

knitr::kable(hfs.unique %>% group_by(County,District) %>% 
  summarise (OIC= sum(OIC...Total, na.rm = T),
             Second_Screener= sum(Second.Screener...Total, na.rm = T),
             Lab_tech= sum(Lab.Tech...Total, na.rm = T),
             CHSS= sum(CHSS...Total, na.rm = T),
             CHV= sum(CHV...Total, na.rm = T),
             Other=sum(Other...Total, na.rm = T),
             Total = sum (Total),
             NTD_cases = sum (X3...Number.of.NTD.patients., na.rm = T)) %>%
    janitor::adorn_totals() , format = 'html') 


```
]
---
## Health workers (from HFs data)


```{r eval=requireNamespace("DT", quietly=TRUE)}

hw<-hfs.unique %>% group_by(County, District,health_facility) %>% 
  summarise (OIC= sum(OIC...Total, na.rm = T),
             Second_Screener= sum(Second.Screener...Total, na.rm = T),
             Lab_tech= sum(Lab.Tech...Total, na.rm = T),
             CHSS= sum(CHSS...Total, na.rm = T),
             CHV= sum(CHV...Total, na.rm = T),
             Other=sum(Other...Total, na.rm = T),
             Total = sum (Total),
             NTD_cases = sum (X3...Number.of.NTD.patients., na.rm = T)
  ) %>% rename (HF=health_facility)

DT::datatable(hw, fillContainer = FALSE, options = list(pageLength = 3),
              rownames = FALSE,
               caption = 'Table 2: Health workers',
              filter = 'top')
```

---
## Health workers survey

```{r}

source("hw.R")

```

.right-column[

Data was collected from **344** Health workers across 3 counties and 6 districts

The number of health workers varies between 90 (Voinjama, Lofa) to 25 (Cavalla, Grand Gedeh)

At county level: Lofa - 184, Margibi - 100, Grand Gedeh - 80

]


.left-column[
```{r}

knitr::kable(hw_distinct %>% group_by(County, District) %>% tally(), format = 'html')

```
]


---
## Health workers survey


.left-column[
**Highest number of surveys**

Martha Tubman Memorial Hospital (Tchien, GG) - 45 surveys

Cotton Tree Health Center (Firestone, Margibi) - 27 surveys

Foya Boma Hospital (Foya, Lofa) - 21 surveys

Tellewoyan Memorial Hospital (Voinjama, Lofa) - 21 surveys

Zeeworth Clinic (Mambah-Kaba, Margibi) - 19 surveys

Janzon Clinic (Cavalla, GG) - 13 surveys

]

.right-column[
```{r fig.width=9, fig.height=6.5}


hw_hf<-hw_distinct %>% group_by(County, District,health_facility) %>% 
  tally() %>%
  arrange(n)


p.hw<-hw_hf %>% ungroup %>%
  mutate(health_facility = fct_reorder(.f=health_facility,
              .x = n, .fun = max, na.rm = T)) %>% 
  ggplot() +
           geom_point(aes(health_facility,n, colour=District)) + 
  facet_wrap(~County) + theme_light() + theme (axis.text.x = element_blank())+
  xlab("Health Facilities")
  
ggplotly(p.hw,tooltip = c("health_facility", "n"))

```
]

---
## Health workers survey

.left-column[

CHA, CHV   -                                            188

Nurse (Nurse assistant, and Midwifery)   -               56

OIC (Screeners & Surveillance Officer)    -              35

Pharmacist (Dispenser)              -                    19

CHSS                               -                     11

Lab Technicians (Lab aid, and Diagnosis officer)    -    11

General Practitioner (PA, MD, and Clinical Director)  -   6

Data Manager (M&E Officer, Data Clarke)            -      1

Others                                  -                17
]

.right-column[
```{r fig.width=8, fig.height=5}

hw_hf_post<-hw_distinct %>% group_by(County, District,health_facility,
                                `3.  What is your professional title?`) %>% 
  tally() %>%
  arrange(n) %>% rename (Job=`3.  What is your professional title?`)

p.hw_post<-hw_hf_post %>% ungroup %>%
  mutate(Job = fct_reorder(.f=Job,
              .x = n, .fun = max, na.rm = T)) %>% 
  ggplot() +
           geom_boxplot(aes(Job,n, colour=District)) + theme_light() + 
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, size=7)) +
  facet_wrap(~County) + xlab("")

p.hw_post
  
#ggplotly(p.hw_post,tooltip = c("Job", "n"))

```
]


---
## Other data

```{r}

source("patients.R")

```

- 1 observation on page 3 of the Health Facility tool (lab) - with incomplete data

- 8 patients from Voinjama: 4 with BU and 4 with Hydrocele
